---
title: "Exercise 15.1"
output: html_document
date: "2023-04-17"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Number 1

A machine produces memory sticks of varying lengths, distributed uniformly between 2 and 12 mm. Memory sticks longer than 10 mm do not meet the design criterion, and must be scrapped.

(a) Calculate the probability that a memory stick will be scrapped.

```{r}
a = 2 
b = 12

scrap <- 2/(b-a)
scrap

```

(b) Simulate 50 memory stick lengths and obtain a histogram of the simulated values. Calculate the simulated mean and variance

```{r}
simulate = runif(50, 2, 12)
round(simulate,3)

mean(simulate)

var(simulate)

hist(simulate, main="Memory stick lengths")
```

## Number 2

Students in an electronic engineering laboratory measure current in using an ammeter. Due to several random factors, the measurement X follows the pdf


(a) Show that, for this to be a genuine probability density, b = 0.15.

```{r}

```
(b) Find the probability that the measurement of the current exceeds 3 A.

```{r}

```
(c) Find E(X).

```{r}

```


## Number 3

In a radio communications system, the phase difference X between the transmitter and receiver is modeled as having a uniform density in [âˆ’ðœ‹,ðœ‹],[âˆ’ðœ‹,+ðœ‹]. Find P(X â‰¤ 0) and P(X â‰¤ ðœ‹âˆ•2)

```{r}

```
